Bird beak's elaboration and exploration

### 2021-05-26 Analysis/02-MCMCglmm_mini_chains.Rmd
reproducible pipeline!

```{r load_beer, eval = TRUE}
set.seed(42)
## Loading beer
library(beer)

@@

## Setting the consensus tree
consensus_tree <- demo_tree[[1]]
```

@@

```{r, parametrise_the_model}
## Set up the parametrising chains models
param_MCMCglmm <- make.mini.chains(data         = demo_data,
                                   dimensions   = c(1:4),
                                   tree         = consensus_tree,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "clade"),
                                   residuals    = "global",
                                   priors       = 0.02,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 10000,
                                       thin   = 100,
                                       burnin = 0))

@@

```{r, get_model_parameters}
## Extract the parameters from the parameter chains
est_params <- extract.parameters(param_chains)
```

@@

```{r, parametrise_the_model}
## The thining parameter
thin <- 100
## The number of samples per chains
samples <- 100

@@

```{r, running_replicates}
## The number of replicates
n_reps <- 10

## Run the required chains
results <- run.mini.chains(mini_chains, replicates = n_reps, path = "../Data/Processed/MCMC/")
```

>>>>

```{r load_beer, eval = TRUE}
set.seed(42)
## Loading beer
library(beer)
library(MCMCglmm)

@@

## Setting the consensus tree
consensus_tree <- demo_tree
```

@@

```{r, parametrise_the_model, eval = TRUE}
## Set up the parametrising chains models
param_MCMCglmm <- make.mini.chains(data         = demo_data,
                                   dimensions   = c(1:4),
                                   tree         = consensus_tree,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "clade"),
                                   residuals    = "global",
                                   priors       = 0.02,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 10000,
                                       thin   = 100,
                                       burnin = 0))

@@

```{r, get_model_parameters, eval = TRUE}
## Extract the parameters from the parameter chains
est_params <- extract.parameters(param_chains)
```

@@

```{r, set_the_mini_chains, eval = TRUE}
## The thining parameter
thin <- 100
## The number of samples per chains
samples <- 100

@@

```{r, running_replicates, eval = TRUE}
## The number of replicates
n_reps <- 10

## Run the required chains
results <- run.mini.chains(mini_chains, replicates = n_reps, path = "../Data/Processed/MCMC/")

## Combining the results as one big MCMC
combined_results <- combine.mini.chains(results)

## Saving the results
save(combined_results, file = "../Data/processed/combined_results.rda")
```
